### 2016-02-18 paper.tex
Discuss Bedon et al (2014) a bit; resolves #61

    \begin{tabular}{c|c|c|c|c|c}
        Name & Rotor type & $N_\mathrm{b}$ & $c/R$ & $Re_D$ & Used in \\ 
        \hline
        Sandia 2 m \cite{Blackwell1976} &  Darrieus  & 2--3 & 0.06--0.09 & $\sim 10^6$ & \cite{Roh2013} \\ 
        Sandia 5 m \cite{Sheldahl1977} &  Darrieus  & 3 & 0.08 & $\sim 10^6$ & \cite{Antheaume2008} \\ 
        Sandia 17 m \cite{Worstell1978} & Darrieus  & 2 & 0.06 & $\sim 10^7$ & \cite{Para1988,Orlandi2015} \\ 
        Sandia 34 m \cite{Ashwill1992} & Darrieus  & 2 & 0.05 & $\sim 10^7$ & \cite{Liu1992,Murray2011}  \\ 
        Strickland \emph{et al.} \cite{Strickland1981} & H & 1--3 & 0.15 & $\sim 10^5$ & \cite{Ponta2001,Scheurich2011b} \\ 
        Laneville and Vitecoq \cite{Laneville1986} & H & 2 & 0.13 & $\sim 10^6$ & \cite{Amet2009} \\ 
        Howell \emph{et al.} \cite{Howell2010} & H & 2--3 & 0.33 & $\sim 10^5$ & \cite{Joo2015} \\ 
        Penna QR5 \cite{Penna2008} & Helical & 3 & ? & $\sim 10^6$ & \cite{Scheurich2011} \\ 
        Mertens \cite{Mertens2003} & H & 2 & 0.21 & $\sim 10^5$ & \cite{Orlandi2015} \\ 
        VAWT 850 \cite{Mays1990} & Tapered H & 2 & 0.05 & $\sim 10^7$ & \cite{Murray2011} \\ 
        UNH-RVAT \cite{Bachant2014-RVAT-baseline} & H & 3 & 0.28 & $\sim 10^6$ & \cite{Michelen2014}
    \end{tabular}

@@

In general, there have been more experiments done with rotors of low $c/R$,
which makes them easier to model, since unsteady dynamic effects are less
influential on the overall performance \cite{Strickland1981}. This is apparent
when examining the effectiveness of numerical models that rely on static foil
coefficient input data, e.g., streamtube and vortex models, which seem to be
most applicable for $c/R \leq 0.1$.

>>>>

    \begin{tabular}{c|c|c|c|c|c}
        Name & Rotor type & $N_\mathrm{b}$ & $c/R$ & $Re_D$ & Used in \\ 
        \hline
        Sandia 2 m \cite{Blackwell1976} &  Darrieus  & 2--3 & 0.06--0.09 & $\sim 10^6$ & \cite{Roh2013,Bedon2014} \\ 
        Sandia 5 m \cite{Sheldahl1977} &  Darrieus  & 3 & 0.08 & $\sim 10^6$ & \cite{Antheaume2008,Bedon2014} \\ 
        Sandia 17 m \cite{Worstell1978} & Darrieus  & 2 & 0.06 & $\sim 10^7$ & \cite{Para1988,Orlandi2015,Bedon2014} \\ 
        Sandia 34 m \cite{Ashwill1992} & Darrieus  & 2 & 0.05 & $\sim 10^7$ & \cite{Liu1992,Murray2011,Bedon2014}  \\ 
        Strickland \emph{et al.} \cite{Strickland1981} & H & 1--3 & 0.15 & $\sim 10^5$ & \cite{Ponta2001,Scheurich2011b} \\ 
        Laneville and Vitecoq \cite{Laneville1986} & H & 2 & 0.13 & $\sim 10^6$ & \cite{Amet2009} \\ 
        Howell \emph{et al.} \cite{Howell2010} & H & 2--3 & 0.33 & $\sim 10^5$ & \cite{Joo2015} \\ 
        Penna QR5 \cite{Penna2008} & Helical & 3 & ? & $\sim 10^6$ & \cite{Scheurich2011} \\ 
        Mertens \cite{Mertens2003} & H & 2 & 0.21 & $\sim 10^5$ & \cite{Orlandi2015} \\ 
        VAWT 850 \cite{Mays1990} & Tapered H & 2 & 0.05 & $\sim 10^7$ & \cite{Murray2011} \\ 
        UNH-RVAT \cite{Bachant2014-RVAT-baseline} & H & 3 & 0.28 & $\sim 10^6$ & \cite{Michelen2014}
    \end{tabular}

@@

In general, there have been more experiments done with rotors of low $c/R$,
which makes them easier to model, since unsteady dynamic effects are less
influential on the overall performance \cite{Strickland1981}. This is apparent
when examining the effectiveness of numerical models that rely on static foil
coefficient input data, e.g., streamtube and vortex models, which seem to be
most applicable for $c/R \leq 0.1$. For example, Bedon \emph{et al.}
\cite{Bedon2014} used a double multiple streamtube momentum model without
dynamic stall corrections to evaluate the effectiveness of various foil
coefficient databases against the Sandia Darrieus turbine experimental data.
Despite using such a simple model, performance predictions were quite accurate
in most conditions except at low tip speed ratio for the 2 m turbine, which had
the highest $c/R$ of all the Sandia rotors, making the dynamic effects more
important. This point highlights the need for more validation data for higher
solidity rotors to ensure numerical models are robust enough to explore unique
cross-flow turbine designs.
